---
title: "Readings"
bibliography: my_lib.bib
csl: cit.csl
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, results = "asis"}
cat('+++')
cat("\n\n")
cat('fragment = \\"content\\"\n\n')
cat('date =\\"', Sys.Date(), '\\"\n\n')
cat('weight = 100\n\n')
cat('+++')
```

## Readings

These are some initial readings about reproducibility and open science, the relationship between rigor and replicability, tools to improve research practices, challenges, and solutions.

### Overview

* @Baker_2016

### Is Research Reproducible?

#### Theoretical

* @Ulrich_2020

#### Empirical

* @Collaboration_2015
* @Stodden_2018
* @Archmiller_2020

### Questionable Research Practices & Researcher Degrees of Freedom

* @John_2012
* @Silberzahn_2018
* @Steegen_2016

### Data Sharing

* @Miyakawa_2020

### Credit

* @Lamprecht_2020
* @Moher_2020

### Pipelines, Automation, & Tools

* @Beaulieu-Jones_2017
* @White_2019

### Diversity, Equity, and Inclusion

* @Bahlai_2019
* @OCSDNet_2019
* @Murphy_2020

### Solutions

* @Markowetz_2015
* @Nosek_2015
* @Lowndes_2017

